---
title: "Homework 1"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## *The Properties of Quadratic Equation*

The quadratic equation takes the general form of $y=ax^2+bx+c$, where a, b and c are known values. "X" is the variable or unkoown. 

```{r include=FALSE}
source('HW01.R')
```

In the previous R-file, I've defined x as a vector, which takes the value of 
```{r}
x
```

Now we will try to examine the six different cases of the quadratic equation when differnt parameters are zeros. 

### When a=0

When the parameter $a=0$, the output we get will be (we can call this $Y1$)
```{r include=FALSE}
Y1=quad(x,0,2,3)
```
```{r}
Y1
```

```{r,echo=FALSE}
plot(x,Y1,"l",col="red")
```

We can see from the graph that when $a=0$, the equation becomes a standard linear equation, where $b$ is the slope and $c$ is the y-intercept.

### When b=0

When the parameter $b=0$, the output we get will be (we can call this $Y2$)
```{r include=FALSE}
Y2=quad(x,2,0,3)
```
```{r}
Y2
```

```{r,echo=FALSE}
plot(x,Y2,"l",col="red")
```

When $b=0$, the graph still looks like a quadratic function with a vertice of $(0,3)$.

### When c=0

When the parameter $c=0$, the output we get will be (we can call this $Y3$)
```{r include=FALSE}
Y3=quad(x,2,3,0)
```
```{r}
Y3
```

```{r,echo=FALSE}
plot(x,Y3,"l",col="red")
```

When $c=0$, the vertice of the graph appears to shift to the left.

### When a and b=0

When the parameter $a$ and $b$ both equal to 0, the output we get will be (we can call this $Y4$)

```{r include=FALSE}
Y4=quad(x,0,0,3)
```
```{r}
Y4
```

```{r,echo=FALSE}
plot(x,Y4,"l",col="red")
```

As you can see, the graph simply becomes a stright horizontal line. 

### When a and c=0

When the parameter $a$ and $c$ both equal to 0, the output we get will be (we can call this $Y5$)

```{r include=FALSE}
Y5=quad(x,0,3,0)
```
```{r}
Y5
```

```{r,echo=FALSE}
plot(x,Y5,"l",col="red")
```

Again, this graph becomes a standard linear equation, where b is the slope, and the intercept is 0. 

### When b and c=0

When the parameter $b$ and $c$ both equal to 0, the output we get will be (we can call this $Y6$)

```{r include=FALSE}
Y6=quad(x,3,0,0)
```
```{r}
Y6
```

```{r,echo=FALSE}
plot(x,Y6,"l",col="red")
```

Now this graph is a normal hyperbola graph with a vertice of $(0,0)$.




## *Conclusion*

We've examined the situations where different parameters are zeros, now let's put all of them onto the same plot to better understand what we've found. 

```{r,echo=FALSE}
plot(x,Y1,"l",xlab="x", ylab="Y",col="red")
lines(x,Y2,col="blue")
lines(x,Y3,col="green")
lines(x,Y4,col="black")
lines(x,Y5,col="gray")
lines(x,Y6,col="yellow")
```

We know that in a quadratic equation, $a$ $b$ and $c$ are parameters or coefficients. The coefficient of $a$ determines the width of the parabola, when it takes the value of 0, it becomes a simple linear equation (refer to the graph with red, black and gray colored lines). $b$ is the "linear" coefficient of $X$, it determines where the vertices will shift to. When it takes the value of 0, the vertices will become $(0,C)$ (refer to the graph with blue and yellow colored lines). The coefficient of $c$ is just the constant, it determines whether the graph shifts upward or downward. When it takes the value of 0, the equation still reamins to be a quadratic equation. 